% !TEX program = xelatex
\documentclass{resume}
\usepackage{graphicx}
\usepackage{tabu}
\usepackage{multirow}
\usepackage{progressbar}
\usepackage{fontspec}
\usepackage{geometry}

%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
\setmainfont{Charter}

\geometry{
  %% body={7in, 14in},
  left=0.5in,
  top=0.7in
}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{WANG Tianchang}

\basicInfo{
  \email{wangtcalex@gmail.com} \textperiodcentered\ 
  \phone{(+86) 188-569-39847 or (+852)60967196} \textperiodcentered\ 
  % \phone{(+852) 6096-7196} \textperiodcentered\ 
  \linkedin[tianchangwang]{www.linkedin.com/in/tianchangwang}
  % \github[github.com/chang2000]{https://github.com/chang2000} 
}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{The Chinese University of Hong Kong}, Hong Kong, China}{2017 -- Present}
\textit{B. S.} in Computer Science(CS), expected July, 2021
\datedsubsection{\textbf{University of California, Berkeley}, Berkeley, U.S.}{2019 Summer}
\textit{Summer Session} in Computer Science(CS)

% \section{\faUsers\ Experience}
% \datedsubsection{\textbf{FLAG Inc.} California, America}{2012 -- Present}
% \role{Summer Intern}{Manager: xxx}
% Brief introduction: xxx.
% \begin{itemize}
%   \item Implemented xxx feature
%   \item Optimized xxx 5\%
%   \item xxx
% \end{itemize}

% \datedsubsection{\textbf{xxx Projects}}{Jan. 2015 -- Present}
% \role{C, Python, Django, Linux}{Individual Projects, collaborated with xxx}
% Brief introduction: xxx
% \begin{itemize}
%   \item Implemented xxx feature
%   \item Optimized xxx 5\%
%   \item xxx
% \end{itemize}

% \datedsubsection{\textbf{\LaTeX\ résumé template}}{May. 2015 -- Present}
% \role{\LaTeX, Maintainer}{Individual Projects}
% An elegant \LaTeX\ résumé template, https://github.com/billryan/resume
% \begin{itemize}
%   \item Easy to be further customized or extended
%   \item Full support for unicode characters (e.g. CJK) with \XeLaTeX\
%   \item FontAwesome 4.5.0 support
% \end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Interested in: Intelligence Science, Web Application Developer
  \item Familiar with: Linux Platform Operation, Group Working Version Control
  % \item Platform: Linux
\end{itemize}


\section{\faHeartO\ Honors and Awards}
\subsection{Academic:}
\datedline{University Exchange Scholarship}{2019, Hong Kong}
\datedline{Shaw College Exchange Scholarship}{2019, Hong Kong}
\datedline{Shaw College Certificate of Academic Merot}{2019, Hong Kong}
\datedline{\textit{\nth{3} Runner-up}, Young Engineers Program (YEP)}{Apr. 2019, Hong Kong}
\datedline{ELITE Stream Scholarship}{Sept. 2018, Hong Kong}
\datedline{Honors at Entrance }{Sept. 2017, Hong Kong}
\datedline{Faculty Admission Scholarship}{Sept. 2017, Hong Kong}
\datedline{University Admission Scholarship}{Sept. 2017, Hong Kong}

\subsection{Extracurricular Activities:}
\datedline{As 组爸 in the Mainland Undergraduate Orientation, CUHK}{Aug. 2018, Hong Kong}
\datedline{Bronze Award, Caring Heart Community Service Project, Shaw College}{Jun. 2018, Hong Kong}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Pacman Game with AI involved}}{Jun. 2019 -- Aug. 2019}
\role{Developer}{Individual Projects}
Use Artificial Intelligence to play the classic game: Pacman https://github.com/chang2000/CS188-Project
\begin{itemize}
  \item Reinforcement Learning involved
  \item Machine Learning Technique involved
\end{itemize}

\datedsubsection{\textbf{YEP of HKIE Project: Vending machine for tools and tools holders}}{Jun. 2019 -- Apr. 2019}
\role{Developer}{Group Projects}
A industrial solution designed for ASM Co. We designed a vending machine to ease the difficulty of selecting and 
managing the tools and tool holders, which is the enssential tool for factory automation.

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: https://chang2000.github.io/blog/
  \item GitHub: https://github.com/chang2000
  \item Languages: English - Fluent, Mandarin - Native speaker, Cantonese - Fluent
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
